simulations

### 2021-09-30 Simulations.Rmd
added wpd analysis

total_distance <- distance %>% 
  mutate(total = hod)

data_pick_one <- total_distance %>% filter(item1 %in% 
                            c(8454221)) %>% group_by(item1) %>% arrange(total) %>% head(5) %>% 
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

@@

@@

data_pick_cust <- bind_rows(
unique(c(data_pick_one$item1,data_pick_one$item2)) %>% as_tibble(),    unique(c(data_pick_two$item1,data_pick_two$item2)) %>% as_tibble(), 
c(11013154, 8495194, 8627007,10109182,10677705,8952846) %>% as_tibble(),
unique(c(data_pick_four$item1,data_pick_four$item2)) %>% as_tibble(),
.id = "design")

@@

```{r heatmap-hod}
sm_hod <- gravitas::create_gran(data_pick, "hour_day")

sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(customer_id, hour_day, general_supply_kwh) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)  %>% 
  left_join(data_pick_cust, by = c("customer_id" = "value"))

ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, ncol(sm_hod_list))]))
nrow_sm <- seq_len(nrow(sm_hod_list))

sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list%>% 
     dplyr::filter(customer_id == customer_id[x]) %>% 
     select(-c(1, ncol(sm_hod_list))) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph, na.rm = TRUE)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "customer_serial_id")

ref_cat <- names(sm_hod_list)[-c(1, ncol(sm_hod_list))] %>% as_tibble() %>% set_names("category") %>%  
  mutate(categories_serial_id = row_number())

ref_cust <- sm_hod_list$customer_id %>% as_tibble()%>% set_names("customer_id")  %>% 
    mutate(customer_serial_id = row_number())

sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(customer_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>%
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "customer_serial_id") %>% 
  select(customer_serial_id, categories_serial_id, category, customer_id, everything())

data_heatmap_hod <- sm_quantiles_ref %>% 
 left_join(data_pick %>% distinct(customer_id)) %>% 
  left_join(data_pick_cust, by = c("customer_id" = "value")) %>% 
  mutate(categories_serial_id = as.factor(categories_serial_id))

data_heatmap_hod %>% 
  ggplot(aes(x = categories_serial_id)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id)) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))

@@

```{r heatmap-moy}
sm_hod <- gravitas::create_gran(data_pick, "month_year")

sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(customer_id, month_year, general_supply_kwh) %>% 
  pivot_wider(names_from = month_year,
              values_from = general_supply_kwh)  %>% 
  left_join(data_pick_cust, by = c("customer_id" = "value"))

ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, ncol(sm_hod_list))]))
nrow_sm <- seq_len(nrow(sm_hod_list))

sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list%>% 
     dplyr::filter(customer_id == customer_id[x]) %>% 
     select(-c(1, ncol(sm_hod_list))) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph, na.rm = TRUE)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "customer_serial_id")

ref_cat <- names(sm_hod_list)[-c(1, ncol(sm_hod_list))] %>% as_tibble() %>% set_names("category") %>%  
  mutate(categories_serial_id = row_number())

ref_cust <- sm_hod_list$customer_id %>% as_tibble()%>% set_names("customer_id")  %>% 
    mutate(customer_serial_id = row_number())

sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(customer_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>%
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "customer_serial_id") %>% 
  select(customer_serial_id, categories_serial_id, category, customer_id, everything())

data_heatmap_moy <- sm_quantiles_ref %>% 
 left_join(data_pick %>% distinct(customer_id)) %>% 
  left_join(data_pick_cust, by = c("customer_id" = "value")) %>% 
  mutate(categories_serial_id = as.factor(categories_serial_id))

data_heatmap_moy %>% 
  ggplot(aes(x = categories_serial_id)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id)) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 12, 2))

@@

```{r heatmap-wkndwday}
sm_hod <- gravitas::create_gran(data_pick, "wknd_wday")

sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(customer_id, wknd_wday, general_supply_kwh) %>% 
  pivot_wider(names_from = wknd_wday,
              values_from = general_supply_kwh)  %>% 
  left_join(data_pick_cust, by = c("customer_id" = "value"))

ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, ncol(sm_hod_list))]))
nrow_sm <- seq_len(nrow(sm_hod_list))

sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list%>% 
     dplyr::filter(customer_id == customer_id[x]) %>% 
     select(-c(1, ncol(sm_hod_list))) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph, na.rm = TRUE)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "customer_serial_id")

ref_cat <- names(sm_hod_list)[-c(1, ncol(sm_hod_list))] %>% as_tibble() %>% set_names("category") %>%  
  mutate(categories_serial_id = row_number())

ref_cust <- sm_hod_list$customer_id %>% as_tibble()%>% set_names("customer_id")  %>% 
    mutate(customer_serial_id = row_number())

sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(customer_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>%
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "customer_serial_id") %>% 
  select(customer_serial_id, categories_serial_id, category, customer_id, everything())

data_heatmap_wkndwday <- sm_quantiles_ref %>% 
 left_join(data_pick %>% distinct(customer_id)) %>% 
  left_join(data_pick_cust, by = c("customer_id" = "value")) %>% 
  mutate(categories_serial_id = as.factor(categories_serial_id))

data_heatmap_wkndwday %>% 
  ggplot(aes(x = categories_serial_id)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id)) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7))

@@

# filtered_distance <- bind_rows(data_pick_one, )
#   
#   data_pick_one

@@

cluster_result <- bind_cols(id = id, group = group) %>% mutate(id =  as.numeric(id))

@@

cluster_result %>% filter(group==1)
cluster_result %>% filter(group==2)
cluster_result %>% filter(group==3)
cluster_result %>% filter(group==4)

@@

```{r data-heatmap-hod}
data_heatmap_hod %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = categories_serial_id)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")
```

```{r data-heatmap-moy}
data_heatmap_moy %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = categories_serial_id)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")
```

```{r data-heatmap-wkndwday}
data_heatmap_wkndwday %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = categories_serial_id)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")

@@

```{r first-try, eval = FALSE}

sm_hod_list_new <- sm_hod_list %>% left_join(cluster_result, by = c("customer_id" = "id"))

sm_hod_list_ncol <- sm_hod_list_new[-c(1, ncol(sm_hod_list_new),(ncol(sm_hod_list_new)-1))]

ncol_sm <- unique(cluster_result$group)
nrow_sm <- seq_len(nrow(sm_hod_list_new))

sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list_new%>% 
     dplyr::filter(group == group[x]) %>% 
     #select(-c(1, ncol(sm_hod_list_new),(ncol(sm_hod_list_new)-1))) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph, na.rm = TRUE)
})  %>% bind_rows(.id = "group_id")
}) %>% bind_rows(.id = "customer_serial_id")

ref_cat <- names(sm_hod_list_ncol) %>% as_tibble() %>% set_names("category") %>%  
  mutate(categories_serial_id = row_number())

ref_cust <- sm_hod_list_new$customer_id %>% as_tibble()%>% set_names("customer_id")  %>% 
    mutate(customer_serial_id = row_number())

sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(customer_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>%
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "customer_serial_id") %>% 
  select(customer_serial_id, categories_serial_id, category, customer_id, everything())

data_heatmap_hod <- sm_quantiles_ref %>% 
 left_join(data_pick %>% distinct(customer_id)) %>% 
  left_join(data_pick_cust, by = c("customer_id" = "value")) %>% 
  mutate(categories_serial_id = as.factor(categories_serial_id))

data_heatmap_hod %>% 
  ggplot(aes(x = categories_serial_id)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id)) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))

@@

>>>>

total_distance <- distance %>% 
  mutate(total = hod)
  #mutate(total = wkndwday/2 + moy/12 + hod/24)

# 8454221 10420689
data_pick_one <- total_distance %>% filter(item1 %in% 
                            c(8454221)) %>% group_by(item1) %>% arrange(total) %>% head(5) %>% 
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

@@

# data_pick_three <- total_distance %>% filter(item1 %in%
#                             c(11013154)) %>% group_by(item1) %>% arrange(total) %>% head(5)%>%
#   mutate(item1 = as.integer(as.character(item1)),
#          item2 = as.integer(as.character(item2)))

@@

# c(11013154, 8495194, 8627007,10109182,10677705,8952846)

data_pick_cust <- bind_rows(
unique(c(data_pick_one$item1,data_pick_one$item2)) %>% as_tibble(),    unique(c(data_pick_two$item1,data_pick_two$item2)) %>% as_tibble(), 
c(11013154, 9345642, 8328008, 8636035,8627007,8454235) %>% as_tibble(),
unique(c(data_pick_four$item1,data_pick_four$item2)) %>% as_tibble(),
.id = "design")

@@

```{r heatmap-hod}
data_heatmap_hod <- quantile_gran(data_pick, "hour_day", quantile_prob_val = c(0.25, 0.5, 0.75)) %>% 
  pivot_wider(names_from = quantiles, values_from = quantiles_values) %>% 
  left_join(data_pick_cust, by = c("customer_id"="value"))

data_heatmap_hod$category <- factor(data_heatmap_hod$category, levels = 0:23)

data_heatmap_hod %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id)) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))

@@

```{r heatmap-moy}
data_heatmap_moy <- quantile_gran(data_pick, "month_year", quantile_prob_val = c(0.25, 0.5, 0.75)) %>% 
  pivot_wider(names_from = quantiles, values_from = quantiles_values) %>% 
  left_join(data_pick_cust, by = c("customer_id"="value"))

data_heatmap_moy$category <- factor(data_heatmap_moy$category, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

data_heatmap_moy %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id)) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

@@

```{r heatmap-wkndwday}
data_heatmap_wkndwday <- quantile_gran(data_pick, "wknd_wday", quantile_prob_val = c(0.25, 0.5, 0.75)) %>% 
  pivot_wider(names_from = quantiles, values_from = quantiles_values) %>% 
  left_join(data_pick_cust, by = c("customer_id"="value"))

data_heatmap_wkndwday$category <- factor(data_heatmap_wkndwday$category, levels = c("Weekday", "Weekend"))

data_heatmap_wkndwday %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id)) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )
```

# Clustering by method 1

@@

@@

cluster_result <- bind_cols(id = id, group = group)

@@

# cluster_result %>% filter(group==1)
# cluster_result %>% filter(group==2)
# cluster_result %>% filter(group==3)
# cluster_result %>% filter(group==4)

@@

```{r data-heatmap-hod}
data_heatmap_hod %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )
```

```{r data-heatmap-hod-group}

data_group <- data_pick %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id"))

data_heatmap_hod_group <- quantile_gran(data_group,
                                  gran1="hour_day",
                                  quantile_prob_val = c(0.25, 0.5, 0.75),
                                  group="group") %>% 
  pivot_wider(names_from = quantiles, values_from = quantiles_values)

data_heatmap_hod_group$category <- factor(data_heatmap_hod_group$category, levels = 0:23)

data_heatmap_hod_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group))) +
  geom_line(aes(y = `50%`, group=group)) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

@@

```{r data-heatmap-moy}
data_heatmap_moy %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )
```

```{r data-heatmap-moy-group}

data_group <- data_pick %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id"))

data_heatmap_moy_group <- quantile_gran(data_group,
                                  gran1="month_year",
                                  quantile_prob_val = c(0.25, 0.5, 0.75),
                                  group="group") %>% 
  pivot_wider(names_from = quantiles, values_from = quantiles_values)

data_heatmap_moy_group$category <- factor(data_heatmap_moy_group$category, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group))) +
  geom_line(aes(y = `50%`, group=group)) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

@@

```{r data-heatmap-wkndwday}
data_heatmap_wkndwday %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("wknd_wday") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

```{r data-heatmap-wkndwday-group}

data_group <- data_pick %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id"))

data_heatmap_wkndwday_group <- quantile_gran(data_group,
                                  gran1="wknd_wday",
                                  quantile_prob_val = c(0.25, 0.5, 0.75),
                                  group="group") %>% 
  pivot_wider(names_from = quantiles, values_from = quantiles_values)

data_heatmap_wkndwday_group$category <- factor(data_heatmap_wkndwday_group$category, levels = c("Weekday", "Weekend"))

data_heatmap_wkndwday_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group))) +
  geom_line(aes(y = `50%`, group=group)) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("wknd_wday") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

# Clustering by method 2

```{r}

elec_600_wpd <- read_rds(here::here("data/algo2-cust600-wpd-rawdata.rds"))

elec_pick <- elec_600_wpd %>% 
  filter(customer_id %in% data_pick_cust$value)

elec_pick_wide <- elec_pick %>% pivot_wider(-c(1, 2), names_from = "x_variable", values_from = wpd)

# robust_scale <-  function(x){
#   (x - stats::median(x))/(stats::IQR(x))
# }

#scaled_var <- apply(elec_pick_wide[-c(1)], 2, robust_scale) %>% as_tibble()

scaled_var <- elec_pick_wide

f <- elec_pick_wide[-1] %>% dist()

group <- f%>% hclust (method = "ward.D") %>% cutree(k=4)

cluster_result_wpd <- bind_cols(id = elec_pick_wide$customer_id, group = group)

ggplot(data = mds %>% as_tibble() %>% mutate(group = cluster_result_wpd$group), 
       aes(x = mds1, y = mds2, color = as.factor(group))) +
  geom_point() +
  geom_text(aes(label = id))

data_pcp <- scaled_var %>% 
  #bind_cols(customer_id =  elec_pick_wide$customer_id) %>%
  left_join(cluster_result_wpd , by = c("customer_id" = "id")) %>% 
  select(customer_id, group, everything()) %>% 
  mutate(group = as.factor(group))

parcoord <- GGally::ggparcoord(data_pcp ,
                   columns = 3:ncol(data_pcp),
                   groupColumn = "group",
                   showPoints = FALSE, 
                   alphaLines = 0.8,
                   order = "anyClass",
                   scale = "globalminmax"
) + ggplot2::theme_bw() +
  scale_color_brewer(palette = "Dark2") + 
  ggplot2::theme(
    plot.title = ggplot2::element_text(size=10)
  )+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 10)) +
  theme(legend.position = "bottom") +
  xlab("") +
  ylab("wpd")

```{r}

data_heatmap_hod %>% 
  #mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result_wpd, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )
```

```{r data-heatmap-hod-group-wpd}

data_group_wpd <- data_pick %>% 
  #mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result_wpd, by = c("customer_id" = "id"))

data_heatmap_hod_group <- quantile_gran(data_group_wpd,
                                  gran1="hour_day",
                                  quantile_prob_val = c(0.25, 0.5, 0.75),
                                  group="group") %>% 
  pivot_wider(names_from = quantiles, values_from = quantiles_values)

data_heatmap_hod_group$category <- factor(data_heatmap_hod_group$category, levels = 0:23)

data_heatmap_hod_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group))) +
  geom_line(aes(y = `50%`, group=group)) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

```{r data-heatmap-moy-wpd}

data_heatmap_moy %>% 
  #mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result_wpd, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )
```

```{r data-heatmap-moy-group-wpd}

data_heatmap_moy_group <- quantile_gran(data_group_wpd,
                                  gran1="month_year",
                                  quantile_prob_val = c(0.25, 0.5, 0.75),
                                  group="group") %>% 
  pivot_wider(names_from = quantiles, values_from = quantiles_values)

data_heatmap_moy_group$category <- factor(data_heatmap_moy_group$category, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group))) +
  geom_line(aes(y = `50%`, group=group)) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

```{r data-heatmap-wkndwday-wpd}
data_heatmap_wkndwday %>% 
  #mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result_wpd, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("wknd_wday") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

```{r data-heatmap-wkndwday-group-wpd}
